RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-10-31 discussion.tex
future work finished

\paragraph{Tool support}

The first possibility is to consider using argumentation semantics \cite{Dung1995} as a way to combine multiple different, possibly inconsistent goal models (cf. \cite{bagheri2011consolidating,MirbelVillata12})

One idea is to capture requirements engineering and software design processes as explicit dialogues between parties~\cite{finkelstein1989multiparty}. Software design discussions Black et al., Prakken and Wierenga.

\paragraph{Empirical validation}

>>>>

\paragraph{Tool support}
The current tool is a prototype that implements the RationalGRL framework in a fairly simple way, that is, by offering the possibility to argue and ask critical questions about a goal model, and then export this goal model for further analysis in jUCMNav. Apart from implementing the tool to include the new fatures described above (e.g. new argument schemes, reasoning with preferences), it is also interesting to think about further possibilities. One idea is to use the tool for collaborative on-line goal modeling, similar to Github: because the renaming (i.e. replacement) and deletion (i.e. disabling) of elements are all logged, it is easy for a stakeholder to continue working on a model that was made by another stakeholder. Furthermore, critical questions can be included for other stakeholders to answer at a later date. As a formal underpinning of this asynchronous communication between users, it would make sense to capture requirements engineering and software design processes as dialogs between parties~\cite{finkelstein1989multiparty,BlackEtal2013}, which are a natural fit with the question-answer format employed in the RationalGRL framework.

\paragraph{Empirical validation}
We have performed a large case study and found more than 200 incidences of arguments and questions. However, what is still lacking is further empirical investigation of whether, and how, the tools and techniques provided by the RationalGRL framework really improve early phase requirements engineering. The complexity of the domain makes focused experiments difficult, but not impossible. For example, Murakannaiah et al.~\cite{murukannaiah2015} provided a realistic but bounded problem for their subjects to solve, and similar experiments are imaginable to test RationalGRL: have two groups solve a goal modelling problem, one using only GRL and one using RationalGRL, and see how they perform. Naturally, the type of problem will greatly influence the outcome. For a simple problem which two people have to solve in an hour, RationalGRL will probably not add much. However, a more complex problem on which multiple persons have to work asynchronously might benefit from the extra tools offered by RationalGRL. Furthermore, the outcome also depends on which part of the set of tools and techniques offered by RationalGRL is tested: the methodology, the tool, or a list of critical questions to serve as reminders during the goal modelling process (cf. \cite{SchriekEtal2016}}).
